---
title: "Data Science for Public Policy"
subtitle: "Assignment 04"
author: "Minji Kang - mk2322 and Ziqiao Shan - zs352"
execute:
  warning: false
format:
  html:
    embed-resources: true
---

```{r}
# install readxl package to read excel file, if needed
# install.packages("readxl")

library(readxl)

library(tidyverse)

library(ggplot2)

# Korea Birth Rate (By Province)

birthrate <-
  read_xlsx("data/birthrate.xlsx") 

birthrate <- birthrate |>
  pivot_longer(
    cols = starts_with("20"),
    names_to = "year",
    values_to = "birthrate"
  )

# Korea Single Household Dataset (By Administrative Region)

```

# First ggplot2 Graph (Bar Chart)

## Breif Explanation:

We used a South Korea's birthrate by region to compare 

```{r}
# First ggplot2 Graph (Bar Chart)
# **Need to add a proper subtitle
# **Need to design it later (font size color etc)

# We used abbreviation of provinces' names, instead of full name. The reason is that the province's names are long.

ggplot(birthrate, mapping = aes(x = Province, y = birthrate, fill = year, color = )) +
  geom_col(width = 0.5) +
  labs(title = "Employment Rate by Age Specification",
       subtitle = "Age 16 and Older + & EMPSTAT as Employed",
       x = "Age Specification",
       y = "Employment Rate",
       caption = "Data Source: National Bureau of Economic Research (NBER)") +
  theme(axis.text.x = element_text(size = 5))

```
## Abbreviations for Each Provinces:
1. Whole country → (Total) Tot.
2. Seoul →	SEO
3. Busan →	BUS
4. Daegu →	DAE
5. Incheon →	INC
6. Gwangju →	GWJ
7. Daejeon →	DJN
8. Ulsan →	ULS
9. Sejong-si →	SJG
10. Gyeonggi-do →	GGD
11. Gangwon-do →	GWD
12. Chungcheongbuk-do →	CCB
13. Chungcheongnam-do →	CCN
14. Jeollabuk-do →	JLB
15. Jeollanam-do →	JLN
16. Gyeongsangbuk-do →	GSB
17. Gyeongsangnam-do →	GSN
18. Jeju →	JEJ

# 2nd ggplot2 Graph (Scatterplot)

```{r}

```

# 3rd ggplot2 Graph (Histogram)

```{r}

```

# 4th ggplot2 Graph (Line Plot)

```{r}

```
